Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-15 docs/manuscript/manuscript.tex
Beginning to write the Data Procedure

\citet{price2019difference} highlights the temporal dynamics of drinking water access and quality in urban slums which
is home to about 1 billion people globally. \citet{price2019difference} discusses the temporal changes in drinking water
access and quality in urban slums may influence on health risks. \citet{price2019difference} believes that monitoring
temporal dynamics should be considered over three interlinked time scales:

\begin{center}
\begin{tabular}{ c c c }
 short-term & medium term & long-term \\ 
  & &  \\  
  & &     
\end{tabular}
\end{center}
\citet{price2019difference} recommends future research to explore the short-term water access and quality monitoring. Also we should learn to recognize the role of socio-cultural factors that may impact the temporal dynamics of safe water access. Our project can pinpoint additional water accessibility variables that can be used to focus to recognize the time variations as well.  
\paragraph{}
\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru. This relates and informs one mode of transportation of clean and accessible water. Our research can make inferences about if the customers receive clean water elsewhere, such as water tankers, kiosks, vendors, etc. Overall, the article found that the percent of households with (IWS) was a few percentage points greater than of the reported utilities. 
\paragraph{}
\citet{deshpande2020mapping} discusses their findings of improved overall water availability and piped water accessibility for the globe (40\% to 50.3\%). \citet{deshpande2020mapping} also found that it was the lowest increase in sub-Saharan Africa, where the accessibility was mostly concentrated in urban regions. \citet{deshpande2020mapping} focuses mostly on understanding trends in diarrhea burden, where the needs are greatest for the improvement of access to safe drinking water and sanitation facilities. Our study can benefit this research by implementing the best and effective modes of transportation of clean water to improve safe drinking water and sanitation. Even with the water pipe access increasing, they can't conclude if the people had clean water as they needed right away. Overall, the access to safe drinking water and sanitation improved globally between 2000 and 2017, but dis-proportionality undermines reaching the SDG goals. 
\paragraph{}
\citet{goal} explains specific targets that have goals and indicators to track global water accessibility. The article quantifies and provides Graphs: safe drinking water, safe sanitation, and hygiene, safe sanitation and hygiene, ambient water quality, water use efficiency, levels of freshwater stress, integrated water management, trans-boundary water cooperation, protect and restore water-related ecosystems, water and sanitation support, local participation in sanitation management. They have many ambitious plans to achieve by 2020 and 2030, and our research can find a correlation to why achieving this may be possible.
% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}
%Another example is \citet{fuller2016tracking}.
%\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru.
%\citet{cassivi2018access} discuss time access...
%\hl{Perhaps insert a table summarizing the various dimensions of water accessibility that have been studied}
%Other examples: \citep{amit2019measuring,ho2014challenge}
\subsection{Gaps and areas for improvement}
We are interested in analyzing the impact of transportation modes (usage/ownership) on water accessibility.

@@

\section*{Data}
\hl{In this section, describe the data sources and the variables, along with data preparation procedures, variable
  selection criteria, etc. You should have a table summarizing the water accessibility variables and their
  definitions. Another table can summarize the explanatory variables (e.g. transportation-related, income-related,
  etc). Also discuss the number of countries, etc. I've started a table as an example. You can add other columns if needed.}

>>>>

\citet{price2019difference} highlights the temporal dynamics of drinking water access and quality in urban slums which
is home to about 1 billion people globally. \citet{price2019difference} discusses the temporal changes in drinking water
access and quality in urban slums may influence on health risks. \citet{price2019difference} believes that monitoring
temporal dynamics should be considered over three interlinked time scales:
\begin{center}
\begin{tabular}{ c c c }
 short-term & medium term & long-term \\ 
  & &  \\  
  & &     
\end{tabular}
\end{center}
\citet{price2019difference} recommends future research to explore the short-term water access and quality monitoring. Also we should learn to recognize the role of socio-cultural factors that may impact the temporal dynamics of safe water access. Our project can pinpoint additional water accessibility variables that can be used to focus to recognize the time variations as well.  
\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru. This relates and informs one mode of transportation of clean and accessible water. Our research can make inferences about if the customers receive clean water elsewhere, such as water tankers, kiosks, vendors, etc. Overall, the article found that the percent of households with (IWS) was a few percentage points greater than of the reported utilities. 
\citet{deshpande2020mapping} discusses their findings of improved overall water availability and piped water accessibility for the globe (40\% to 50.3\%). \citet{deshpande2020mapping} also found that it was the lowest increase in sub-Saharan Africa, where the accessibility was mostly concentrated in urban regions. \citet{deshpande2020mapping} focuses mostly on understanding trends in diarrhea burden, where the needs are greatest for the improvement of access to safe drinking water and sanitation facilities. Our study can benefit this research by implementing the best and effective modes of transportation of clean water to improve safe drinking water and sanitation. Even with the water pipe access increasing, they can't conclude if the people had clean water as they needed right away. Overall, the access to safe drinking water and sanitation improved globally between 2000 and 2017, but dis-proportionality undermines reaching the Sustainable Development Goals. 
\citet{goal} explains specific targets that have goals and indicators to track global water accessibility. The article quantifies and provides Graphs: safe drinking water, safe sanitation, and hygiene, safe sanitation and hygiene, ambient water quality, water use efficiency, levels of freshwater stress, integrated water management, trans-boundary water cooperation, protect and restore water-related ecosystems, water and sanitation support, local participation in sanitation management. They have many ambitious plans to achieve by 2020 and 2030, and our research can find a correlation to why achieving this may be possible.
% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}
%Another example is \citet{fuller2016tracking}.
%\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru.
%\citet{cassivi2018access} discuss time access...
%\hl{Perhaps insert a table summarizing the various dimensions of water accessibility that have been studied}
%Other examples: \citep{amit2019measuring,ho2014challenge}
\subsection*{Gaps and areas for improvement}
We are interested in analyzing the impact of transportation modes (usage/ownership) on water accessibility.

@@

\section*{Data}
\hl{In this section, describe the data sources and the variables, along with data preparation procedures, variable
  selection criteria, etc. You should have a table summarizing the water accessibility variables and their
  definitions. Another table can summarize the explanatory variables (e.g. transportation-related, income-related,
  etc). Also discuss the number of countries, etc. I've started a table as an example. You can add other columns if needed.}
\subsection{Data Preparation}

Data structure this study were collected from the Demographic Health Survey (DHS) program. We used the STATCompiler from the DHS Program to develop customized table based on foucsing on water, transportation, and wealth indicators across more than 90 countries and across all time frame.

Both the waterpoint census and household surveys were undertaken by trained local enumerators and delivered in local languages, predominantly Swahili and Digo. Prior to data collection, research permits and approvals were obtained from the Government of Kenya's National Council of Science and Technology and the Central University Research Ethics Committee at the University of Oxford.
